graphsim: An R package for simulating gene expression data from graph structures of biological pathways

### 2020-06-02 paper/paper.Rmd
update paper figures

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    keep_tex: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: 30 April 2020
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---

>>>>

---
title: 'graphsim: An R package for simulating gene expression data from graph structures of biological pathways'
output:
  rmarkdown::pdf_document:
    fig_crop: no
    keep_md: TRUE
    keep_tex: TRUE
    fig_caption: yes
tags:
  - R
  - gene-expression
  - simulation
  - genomics
  - pathway
  - network
authors:
  - name: S. Thomas Kelly
    email: "tom.kelly@postgrad.otago.ac.nz, tom.kelly@riken.jp"
    orcid: 0000-0003-3904-6690
    affiliation: "1, 2" # (Multiple affiliations must be quoted)
  - name: Michael A. Black
    email: mik.black@otago.ac.nz
    orcid: 0000-0003-1174-6054
    affiliation: "1"
affiliations:
 - name: "Department of Biochemistry, University of Otago, PO Box 56, Dunedin 9054, New Zealand"
   index: 1
 - name: "RIKEN Center for Integrative Medical Sciences, Suehiro-cho-1-7-22, Tsurumi Ward, Yokohama, Kanagawa 230-0045, Japan"
   index: 2
date: "`r  format(Sys.time(), '%d %B %Y')`"
bibliography: paper.bib
header-includes:
  - \usepackage{caption}
 # - \usepackage{subfig}
---
